%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./profile}
\name{Zheng}{Ma}
\position{Golomb Visiting Assistant Professor of Mathematics}
\address{150 N. University Street, West Lafayette, IN 47907-2067, USA}

\mobile{(+1) 765-337-8766}
\email{ma531@purdue.edu}
\homepage{https://www.math.purdue.edu/people/bio/ma531}
\github{mayuyu}
% \linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Recruitment Committee}
  {Shanghai Jiao Tong University\\No. 800 Dongchuan Road\\Shanghai 200240, China}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Tenure-Track Position}
% How the letter is opened
\letteropening{Dear Committee Members,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Zheng Ma~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

My name is Zheng Ma and I am currently a Golomb Visiting Assistant Professor at Purdue University in the Department of Mathematics. I wish to apply for a tenure-track faculty position at School of Mathematical Sciences and Institute of Natural Sciences at Shanghai Jiao Tong University.

My current research interests mainly lie in the theoretical foundations and general theory of machine learning, as well as the applications of deep learning in computational physical problems. With a computational PDE background, I have worked on the model reduction of kinetic equations using deep neural networks, the theoretical understandings of machine learning by F-principle. Besides, I have also developed fast algorithms for kinetic equations and efficient schemes for uncertainty quantification. My long term research agenda is to develop efficient machine learning based methods to solve different kinds of physical problems. By building new machine-learned physical models and designing novel algorithms, I hope to solve interesting problems coming from real applications.

School of Mathematical Sciences at SJTU is a wonderful place for people doing not only mathematics but also sciences in general. The atmosphere is free and open where there are many talented young researchers and prestigious senior professors to talk and work with. This is also the place where I got my B.S. and Ph.D. and I know we have lots of excellent students. I am very eager to come back to work with my former professors and also my classmates.

I have enclosed my CV and Research Statement. I am more than willing to answer any of your questions concerning my research and I will certainly cherish the great opportunity of working with many researchers to advance my knowledge. Thank you for your consideration.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
